Taking uncertainty in word embedding bias estimation seriously: a  bayesian

### 2022-04-25 paperDraft/outdated/paperDraft3.Rmd
added model for jobs and cleaned the paperDraft folder.

---
title: 'Taking uncertainty in word embedding bias estimation seriously: a  bayesian
  approach'
author: "Alicja Dobrzeniecka and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/cosineReferences1.bib
csl: ../references/apa-6th-edition.csl
---

>>>>

---
title: 'Taking uncertainty in word embedding bias estimation seriously: a  bayesian
  approach'
author: "Alicja Dobrzeniecka and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
classoption: dvipsnames,enabledeprecatedfontcommands, twocolumn
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/cosineReferences1.bib
csl: ../references/apa-6th-edition.csl
---
